\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-02 letter.tex
add paragraphs to letter for E1,E8,R1,R4

@@

@@

Referee's point $\#1$ (``Introduction is derailing at the start''):

@@

Referee's point $\#4$ (``Strong language regarding contribution''):

>>>>

Editor's point $\#$1: I have revised the introduction according to the formula you suggested. I have toned down considerably the claims about the PFS puzzle as both you and the referee suggest; they are now at the very end of the introduction and in a soft way in the abstract.

@@

Editor's point $\#8$: I agree that my model does not nest PFS. The discussion in the new Section 2.4, footnote 17 and Section 5.2 is meant to highlight the similarities and differences. I hope that I have addressed your concerns about over-selling the contribution relative to the PFS puzzle so that this is no longer an issue.

@@

Referee's point $\#1$ (``Introduction is derailing at the start''): I agree and I thank you for your detailed suggestions about how to reformulate the introduction and incorporate a toned-down discussion about the PFS puzzle. Please see respone to Editor's point $\#$1 for logistics.

@@

Referee's point $\#4$ (``Strong language regarding contribution''): I agree. Please see response to Editor's point $\#$1.
